Fusing Filters with Integer Linear Programming

### 2014-04-18 2014betterfusionforfilters/section/01-Introduction.tex
intro: update var names in normalize2 example to match diagram

However, many programs \emph{do} contain opportunities for fusion, if we only knew which opportunities to take. The following example offers \emph{several} unique, but mutually exclusive approaches to fusion. Figure~\ref{f:normalize2-cluterings} on the next page shows some of the possibilities.
\begin{code}
 normalize2 :: Array Int -> Array Int
 normalize2 us
  = let sum1 = fold   (+)  0   us
        gts  = filter (> 0)    us
        sum2 = fold   (+)  0   gts
        nor1 = map    (/ sum1) us
        nor2 = map    (/ sum2) us
    in (nor1, nor2)
\end{code}

>>>>

However, many programs \emph{do} contain opportunities for fusion, if we only knew which opportunities to take. The following example offers \emph{several} unique, but mutually exclusive approaches to fusion. Figure~\ref{f:normalize2-cluterings} on the next page shows some of the possibilities.
\begin{code}
 normalize2 :: Array Int -> Array Int
 normalize2 xs
  = let sum1 = fold   (+)  0   xs
        gts  = filter (> 0)    xs
        sum2 = fold   (+)  0   gts
        ys1  = map    (/ sum1) xs
        ys2  = map    (/ sum2) xs
    in (ys1, ys2)
\end{code}
